### 2020-05-27 system-model.tex
:triangular_flag_on_post: Algorithm on FF-IRS

				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I\\

@@

				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P\\

@@

				\State \textbf{Input} $P, \bar{R}, \boldsymbol{h}$ by \ref{eq:h_k}, \ref{eq:theta}
				\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$

@@

					\Until $\lvert R^{(i)}-R^{(i-1)} \rvert \le \epsilon$

@@

					\State Generate CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$

@@

				t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})

@@

					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
					&\quad+\frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
					&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}

@@

					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\right\}\\

@@

					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\\
					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{I/P}^{(i)}\right)\\

@@

					& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I,0}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P,0}^{(i)})\\

@@

					& = \mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\\
					& - \frac{3}{8} \beta_4 (\rho^{(i)})^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (i-1)} (t_{I,n}^{\prime (i-1)})^* + t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^* \\
					& - \frac{3}{2} \beta_4 (\rho^{(i)})^2 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}

@@

			\begin{equation}\label{eq:A_I}

@@

					& = \frac{k_2 \rho^{(i-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (i-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (i-1)}\boldsymbol{M}_{n}^H\right) \\
					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (i-1)}\boldsymbol{M}_{0}
			\begin{equation}\label{eq:A_P}

@@

					& = \frac{k_2 \rho^{(i-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (i-1)}\boldsymbol{M}_{n}^H \\
					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (i-1)}\boldsymbol{M}_{0}
			Plug \ref{eq:z_waveform_approx} into problem \ref{op:temp5} and solve it by iterative interior-point method. Given the optimal waveform matrices $\boldsymbol{W}_I$ and $\boldsymbol{W}_P$, the best rank-1 solution $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$ can be obtained through randomization method. Details are omitted here. The algorithm for the waveform optimization subproblem is summarized in Algorithm ~.

			\begin{algorithm}
				\caption{Waveform Optimization}
				\label{alg:waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\boldsymbol{V}$
					\State \textbf{Initialize} $k=0$, $\boldsymbol{w}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $k = k + 1$
					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I,k} and \ref{eq:A_P,k}
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:temp5}
					\State Update auxiliary $t_{I/P,n}^{\prime (k)} \forall n$ by \ref{eq:t'} for SCA
					% \Until $\lVert \boldsymbol{W}_I^{(i)} - \boldsymbol{W}_I^{(k - 1)} \rVert_F / \lVert \boldsymbol{W}_I^{(i)} \rVert_F \le \epsilon$
					\Until $R^{(i)}-R^{(i-1)} \le \epsilon$
					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{N}) \ \forall r$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r \ \forall r$ and corresponding matrices $\boldsymbol{W}_{I/P,r}=\boldsymbol{w}_{I/P,r}\boldsymbol{w}_{I/P,r}^H  \ \forall r$
					\State Select the best solution pair $\boldsymbol{W}_{I,r}^\star, \boldsymbol{W}_{P,r}^\star$ for problem \ref{op:temp5} and corresponding $\boldsymbol{w}_{I,r}^\star, \boldsymbol{w}_{P,r}^\star$
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}

		% * It holds that $\boldsymbol{M}_{I/P,0} \succeq 0$ and $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$ for $n{\ne}0$.

		% To tackle the non-convex current constraint, we expand and rewrite the coupled channel terms in \ref{eq:z_k_truncated} as
		% \begin{equation}
		% 	\begin{split}
		% 		{h_{n_3}^*}{h_{n_1}}
		% 		&=(h_{D,n_3}^*+\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*)(h_{D,n_1}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*})\\
		% 		&={h_{D,n_1}}{h_{D,n_3}^*}+{h_{D,n_1}}\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*}h_{D,n_3}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*}\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*\\
		% 		&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_3,n_1}\bar{\boldsymbol{v}}^*\\
		% 		&=\mathrm{Tr}(\boldsymbol{R}_{n_3,n_1}\boldsymbol{V}^*)
		% 	\end{split}
		% \end{equation}
		% where
		% \begin{equation}
		% 	\boldsymbol{R}_{n_3,n_1}=
		% 	\begin{bmatrix}
		% 		\boldsymbol{\Phi}_{n_1}^*\boldsymbol{\Phi}_{n_3}^T & \boldsymbol{\Phi}_{n_1}^*{h_{D,n_3}^*} \\
		% 		h_{D,n_1}{\boldsymbol{\Phi}_{n_3}^T}               & h_{D,n_1}{h_{D,n_3}^*}
		% 	\end{bmatrix}
		% \end{equation}
		% Similarly, we have ${h_{n_4}^*}{h_{n_2}}=\mathrm{Tr}(\boldsymbol{R}_{n_4,n_2}\boldsymbol{V}^*)$ and ${h_n^*}{h_n}=\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)$. Thus, \ref{eq:z_k_truncated} is equivalent to
		% \begin{figure*}[b]
		% 	\hrule
		% 	\begin{equation}\label{eq:z_k_su_temp}
		% 		\begin{split}
		% 			z
		% 			&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)(\boldsymbol{w}_{I,n}^H\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{w}_{P,n})}\\
		% 			&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\mathrm{Tr}(\boldsymbol{R}_{n_3,n_1}\boldsymbol{V}^*)\mathrm{Tr}(\boldsymbol{R}_{n_4,n_2}\boldsymbol{V}^*)\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{w}_{P,n_2})\right)\\
		% 			&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)^2(\boldsymbol{w}_{I,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{w}_{P,n})}
		% 		\end{split}
		% 	\end{equation}
		% \end{figure*}
	\end{subsection}

	% % ? AO: optimize weights with given phase shifts
	% To tackle the non-convex current constraint, we introduce a channel matrix $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$ whose $(n_1,n_2)$ entry equals
	% \begin{equation}
	% 	\begin{split}
	% 		{h_{n_1}^*}{h_{n_2}}
	% 		&=(h_{D,n_1}^*+\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*)(h_{D,n_2}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*})\\
	% 		&={h_{D,n_2}}{h_{D,n_1}^*}+{h_{D,n_2}}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}h_{D,n_1}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*\\
	% 		&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*\\
	% 		&=\mathrm{Tr}(\boldsymbol{R}_{n_1,n_2}\boldsymbol{V}^*)
	% 	\end{split}
	% \end{equation}
	% where
	% \begin{equation}
	% 	\boldsymbol{R}_{n_1,n_2}=
	% 	\begin{bmatrix}
	% 		\boldsymbol{\Phi}_{n_2}^*\boldsymbol{\Phi}_{n_1}^T & \boldsymbol{\Phi}_{n_2}^*{h_{D,n_1}^*} \\
	% 		h_{D,n_2}{\boldsymbol{\Phi}_{n_1}^T}               & h_{D,n_2}{h_{D,n_1}^*}
	% 	\end{bmatrix}
	% \end{equation}
	% On top of this, $\boldsymbol{M}_n$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and nulls the remaining entries. It holds that $\boldsymbol{M}_0 \succeq 0$ and $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}. Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_waveform}.
	% \begin{figure*}[b]
	% 	\hrule
	% 	\begin{equation}\label{eq:z_k_waveform}
	% 		\begin{split}
	% 			z
	% 			&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
	% 			% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
	% 			% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
	% 			&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H}\\
	% 			&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)}
	% 		\end{split}
	% 	\end{equation}
	% \end{figure*}
	% We then introduce auxiliary vectors $\boldsymbol{t}_{I/P}=[t_{{I/P},0},\dots,t_{{I/P},N-1}]^T \in \mathbb{C}^{N \times 1}$ with $t_{{I/P},n}=\boldsymbol{w}_{I/P}^H\boldsymbol{M}_n\boldsymbol{w}_{I/P}=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{W}_{I/P})$ and transform \ref{eq:z_k_waveform} to
	% % and define coefficient matrix $\boldsymbol{A}_0=\mathrm{diag}\{\}$
	% \begin{equation}\label{eq:z_k_su_compact}
	% 	\begin{split}
	% 		z
	% 		&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
	% 		&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P-2t_{I,0}t_{I,0}^*-t_{P,0}t_{P,0}^*)\\
	% 		&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
	% 	\end{split}
	% \end{equation}

	% A semidefinite programming (SDP) problem is then formulated by dropping the rank-one constraint

	% which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
	% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
	% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
	% Although the problem is non-convex, the target function can be reformulated using the triangle inequality
	% \begin{equation}
	% 	\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
	% \end{equation}
	% where the equality holds if and only if the direct and IRS-aided links align with each other. In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$. Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
	% \begin{equation}
	% 	\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
	% \end{equation}
	% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_truncated} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
	% \begin{equation}\label{eq:phi_n}
	% 	\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
	% \end{equation}

\end{section}

>>>>

				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I\\

@@

				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P\\

@@

				\State \textbf{Input} $P, \bar{R}, \theta_l \ \forall l$
				\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}, \boldsymbol{h}$ by \ref{eq:h_k}, \ref{eq:theta}

@@

					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$

@@

					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$

@@

				t_{I/P,n}' = \rho \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\rho \boldsymbol{H}_n^*\boldsymbol{W}_{I/P})

@@

					&=\frac{1}{2} \beta_2 (t'_{I,0}+t'_{P,0})\\
					&\quad+\frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
					&\quad+\frac{3}{2} \beta_4 t'_{I,0}t'_{P,0}

@@

					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\right\}\\

@@

					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\\
					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{I/P}^{(i)}\right)\\

@@

					& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I,0}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P,0}^{(i)})\\

@@

					& = \rho^{(i)}\left(\mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\right)\\
					& \quad - \frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (i-1)} (t_{I,n}^{\prime (i-1)})^* + t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\
					& \quad - \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}

@@

@@

				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^*\nonumber\\
				& \quad + \frac{3}{4} \beta_4 \sum_{n=-N+1}^{N-1} (t_{I,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{I,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\nonumber\\
				& \quad + \frac{3}{2} \beta_4 t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_I}\\

@@

				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^*\nonumber\\
				& \quad + \frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\nonumber\\
				& \quad + \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_P}
				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method. $\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can be approximated via randomization method as in section \ref{se:fs_irs}. The algorithm is summarized in Algorithm \ref{al:fs_waveform}.

			\begin{algorithm}
				\caption{Waveform Optimization}
				\label{alg:waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\bar{R},P,\theta_l \ \forall l$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I} and \ref{eq:A_P}
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
					\State Update auxiliary $t_{I/P,n}^{\prime (k)} \forall n$ by \ref{eq:t'} for SCA
					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{N}) \ \forall q$
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ for problem \ref{op:su_waveform} and corresponding $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}
	\end{subsection}
\end{section}
